Simulation Deep Dive

### 2021-10-29 Simulation Deep Dive.Rmd
Adds changes to markdown document

tsne1 <- readRDS("C:/Users/paulh/Documents/Doctoral Work/InfluenceInMaps/2021-10-24_simulationCorrelated_tsne_list2.RDS")
mds1 <- readRDS("C:/Users/paulh/Documents/Doctoral Work/InfluenceInMaps/2021-10-24_simulationCorrelated_mds_list2.RDS")

>>>>

tsne1 <- readRDS("2021-10-29_simulationCorrelated_tsne_list2.RDS")
mds1 <- readRDS("2021-10-29_simulationCorrelated_mds_list2.RDS")
